Twists of supersymmetric gauge theories

### 2020-01-13 paper.tex
compiler error
note on changes to make

\tikzstyle{s16} = [rectangle, rounded corners, text centered, innersep=0pt, draw=black,fill=red!30]
\tikzstyle{s16chiral} = [s16, dashed]
\tikzstyle{s8} = [rectangle, rounded corners, text centered, draw=black,fill=orange!30]
\tikzstyle{s4} = [rectangle, rounded corners, text centered, draw=black,fill=yellow!30]
\tikzstyle{s2chiral} = [rectangle, dashed, rounded corners, text centered, draw=black,fill=green!30]
\tikzstyle{dimension} = [circle, text centered, text width=0.7cm, minimum height=0.7cm, draw=black]
\tikzstyle{arrow} = [thick,->,>=stealth]

@@

>>>>

\tikzstyle{s16} = [rectangle, rounded corners, text centered, draw=black,fill=red!30]
\tikzstyle{s16chiral} = [s16, dashed]
\tikzstyle{s8} = [rectangle, rounded corners, text centered, draw=black,fill=orange!30]
\tikzstyle{s4} = [rectangle, rounded corners, text centered, draw=black,fill=yellow!30]
\tikzstyle{s2chiral} = [rectangle, dashed, rounded corners, text centered, draw=black,fill=green!30]
\tikzstyle{dimension} = [circle, text centered, text width=0.7cm, minimum height=0.7cm, draw=black]
\tikzstyle{arrow} = [thick,->,>=stealth]

@@

\chris{Todo: would be more correct to remove the generic rank 2 twist in 3d, same as the 3d A twist (dual RW).  I should do this in the tables and the diagrams.  Also todo: change the labels of orbits to A and B.}
